---
title: "using_wiodnet"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{using_wiodnet}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Using WIODnet

```{r setup}
library(WIODnet)
```
This package aims to help researchers using [WIOD
data](http://www.wiod.org/home). WIOD (World Input Output Data) is a
collection of input output tables covering 43 countries and a model for
the rest of the world (RoW), 56 sectors classified according to he
International Standard Industrial Classification revision 4 (ISIC
Rev. 4) for the period of 2000-2016.

This package download the zip file provided at the [download
section](http://www.wiod.org/database/wiots16), check its integrity,
create long tables, record them on the working directory and carry out
network analysis and finally create a panel data comprising all
information obtained from WIOD tables.

Using the isic parameter in the functions; it is possible to obtain
final panel data with industries aggregated at different levels. All
nodes are country-industry pairs.

1. isic = 0

    There is no aggregation in industries. All nodes are
    country-industry pairs as given in the original files.
   
2. isic = 1

   The aggregation is carried out at the level of ISIC 1 digit code. 

3. isic = 2

   The aggregation is only made for the manufacturing industry according
   to the [Eurostat technology intensity
   classification](https://ec.europa.eu/eurostat/statistics-explained/index.php/Glossary:High-tech_classification_of_manufacturing_industries)


WIODnet package provides four functions to users. All functions creates
directories and the final panelWIOD(isic) gives panel data in csv
format. The last function getCountryWIOD provides a panel data in which
there is no industry, all I-O is country based.

1. getWIOD(isic) this function download the WIOD data into
   wiod_original_data and creates long tables for each year in
   wiod_long_data.

2. netWIOD(isic) makes the network calculation on the long tables which
   are created with getWIOD().

3. panelWIOD(isic) merges all long tables and provide a single panel data
   file in csv.

4. getCountryWIOD() use WIOD data to provide a panel data consisting of
   countries.

If you are using this package multiple times, better to stick to work
always on the same directory, else you will download the same +600 MB
data from the WIOD server. 
